\documentclass[12pt]{article}
\usepackage{amsfonts, amssymb, amsthm}
\usepackage{amsmath}

\pagestyle{myheadings}
\markright{Simon Kurgan\hfill\today\hfill}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]

\begin{document}

\section{Introduction}

\begin{theorem}
For all integers $a$ and $b$ with $b > 0$, there exist unique integers $q$ and $r$ such that $a = bq + r$, and $0 \leq r < b$.
\end{theorem}

\begin{proof}[Proof:]
Let $a = -5$ and $b = 2$. Then,
\[
-5 = 2 \times (-3) + 1
\]
So, for $a = -5$ and $b = 2$, there exists a unique $q$ and $r$ belonging to the set of integers such that $a = 2q + r$ with $0 \leq r < 2$ (i.e., $r = 0$ or $1$).

By Theorem 16, every integer is either odd or even.
\end{proof}

\begin{corollary}
For any integer $a$, $b$ with $b > 1$, there exists a unique $r \in \mathbb{Z}$ such that $a = r \pmod{b}$ and $0 \leq r < b$.
\end{corollary}

When $b = 3$, for any $z \in \mathbb{Z}$, there exists a unique integer $r$ such that $a \equiv r \pmod{3}$ and $r \in \{0, 1, 2\}$.

\newpage

\begin{theorem}
For every integer $n$, $n^3 \equiv n \pmod{3}$.
\end{theorem}

\begin{proof}[Proof:]
By Corollary 1, we only have one of the three cases:

\textbf{Case 1:} $n \equiv 0 \pmod{3}$

\[
n^3 \equiv n \pmod{3} \longrightarrow  3 \mid (n^3 - n)
\]
\[
3 \mid (n^3 - n) \longrightarrow (n)(n - 1)(n - 1)
\]
By Theorem 20, we have $n^3 \equiv 0^3 \pmod{3}$.

\textbf{Case 2:} $n \equiv 1 \pmod{3}$

Similarly, $n = n^3 \pmod{3}$.

\textbf{Case 3:} $n \equiv 2 \pmod{3}$

\end{proof}

\newpage

\begin{theorem}
Let $n \in \mathbb{Z}$. Then $n$ is even if and only if $n^2$ is even. Similarly, $n$ is odd if and only if $n^2$ is odd.
\end{theorem}

\begin{proof}[Proof:]
\textbf{$\longrightarrow$}

Suppose $n$ is even. Goal: $n^2$ is even.

Then $n = 2k$ for some $k \in \mathbb{Z}$.

So, $n^2 = (2k) \times n = 2(kn)$, where $kn \in \mathbb{Z}$ by the closure of $\mathbb{Z}$.

Hence, $n^2$ is even.

\textbf{$\longleftarrow$}

Need to prove: if $n^2$ is even, then $n$ is even.

Contrapositive: If $n$ is not even, then $n^2$ is not even.

By Theorem 16, if an integer is not even, then it is odd.

Suppose $n$ is odd. Then $n = 2k + 1$ for some $k \in \mathbb{Z}$.

\[
\text{So, } n^2 = (2k + 1)^2 = 4k^2 + 4k + 1 = 2(2k^2 + 2k) + 1.
\]

Since $2k^2 + 2k \in \mathbb{Z}$, $n^2$ is odd.
\end{proof}

\newpage

\section{Revisit}

Let $x \in \mathbb{R}$. We say $x$ is rational if there exist integers $p$ and $q$ with $q \neq 0$ such that $x = \frac{p}{q}$. We say $x$ is irrational if it is not rational.

\begin{theorem}
$\sqrt{2}$ is irrational.
\end{theorem}

\begin{proof}[Proof:]
There exist $p, q \in \mathbb{Z}$ such that $\sqrt{2} = \frac{p}{q}$, $q \neq 0$.

$2 = \frac{p^2}{q^2} \Rightarrow 2q^2 = p^2$

$\Rightarrow p^2$ is even

$\Rightarrow p$ is even ($p = 2k$, where $k \in \mathbb{Z}$)

$\Rightarrow 2q^2 = (2k)^2 = 4k^2$.

$q^2 = 2k^2$

$\Rightarrow q^2$ is even

$\Rightarrow q$ is even ($q = 2L$, where $L \in \mathbb{Z}$)

$\sqrt{2} = \frac{p}{q}$ p is negative and $-p$ is positive.
\end{proof}

\textbf{Remark:} We use proof by contradiction, then we prove that the well-ordering property is contradicted.

\end{document}
